Master's Project Journal

### 2018-10-21 tex_files/Journal.tex
hournal update

Eventually went for 1000 -> gives 1.58 MHz w/ inv chain. Works as expected. ~315 ps gate delay.

>>>>

Eventually went for 1000 -> gives 1.58 MHz w/ inv chain. Works as expected. ~315 ps gate delay.
\section*{Jitter detection}
Started the week attempting to implement a system using the FPGA to measure jitter of the clock. Prior to this I implemented the ability to tune the frequencies of the oscillators. The RO was given 4 bit control, removing an extra pair of inverters each time. The PAccum was given 9 bit control.
When I tried to do jitter detection I ran into a pair of problems. The first of these is my resolution was going to suffer.
At 5 MHz RO clock Tnom is 200 nsec. Running the FPGA at 500 MHz gives 2 ns resolution. Period change through two oscillators is 1.2 ns. Cannot tell 3! jumps apart.
Switched to using the agilent 4 GS/s scope, it has 250 psec resolution.
Collected data friday, ran it through matlab, got some basic jitter calculations done.
Wrote a bash script that implements a GPL c library that interacts with the scope over ethernet.
Hopefully it works and can be used to automate datacapture process
Will test Monday.
